\href{https://github.com/uds-datalab/PDBF}{PDBF} Documentation

### 2016-02-10 minimal.tex
Converted windows to unix line-endings
Version 1.2.1 - Bugfixes - renamed signatureplot to compareToBest
- fixed a bug that sometimes made the xref fixing fail - minified all js and css files - updated lot of javascript libraries to up to date versions

\dbSQLText{CREATE TABLE test(a int, b int, c int); INSERT INTO test VALUES(1, 1, 1); INSERT INTO test VALUES(2, 2, 4); INSERT INTO test VALUES(3, 3, 8); INSERT INTO test VALUES(4, 4, 16);}
%\dbSQLFile{somedb.sql}
%\dbSQLJDBC{jdbc:postgresql://localhost:5432/postgres}{postgres}{test}{testtable}%
%\dbCSVFile{result.csv}{test}

\begin{document}
\noindent
\sql{SELECT * FROM test;}\\[3pt]
The table ``test'' contains \dataText{SELECT COUNT(*) FROM test;} tuples.\\[3pt]
The following points are linked to the chart on the left side below: \dataText[linkTo=testname, linkSelector=2, linkLabel=Value at 2]{SELECT * FROM test WHERE a=2;}, \dataText[linkTo=testname, linkSelector=3, linkLabel=Value at 3]{SELECT * FROM test WHERE a=3;}.\\[3pt]
\chart[width=0.45\textwidth, height=0.3\textwidth, logscale=true, chartType=line, name=testname]{SELECT * FROM test;}
\chart[width=0.45\textwidth, height=0.3\textwidth, chartType=bar]{SELECT * FROM test;}\\[3pt]
{\fontfamily{phv} \tiny \selectfont
\noindent
Change the font before this line to Helvetica and fontsize to tiny.\\[3pt]
\chart[width=0.6\textwidth, height=0.25\textwidth, chartType=signatureplot]{SELECT b FROM test;}\\[3pt]
\multiplotChart[width=0.6\textwidth, height=0.5\textwidth, xCount=2, yCount=2, yValues={["b", "b*2"]}, xValues={["a <= 2", "a > 2"]}, topArr={["a smaller or equal 2", "a greater 2"]}, yFirst]{SELECT a,? FROM test WHERE ?;}\\[3pt]
\pivotTable[width=0.10\textwidth, height=0.15\textwidth, rows={["a"]}, aggregationattribute=b]{SELECT * FROM test;}
\dataTable[verticalLines=i, horizontalLinesHeader=b hh, horizontalLinesBody=i]{SELECT * FROM test;}\\[3pt]
}
\end{document}

>>>>

\dbSQLText{CREATE TABLE test(a int, b int, [attribute with space] int); INSERT INTO test VALUES(1, 1, 1); INSERT INTO test VALUES(2, 2, 4); INSERT INTO test VALUES(3, 3, 8); INSERT INTO test VALUES(4, 4, 16);}
%\dbSQLFile{somedb.sql}
%\dbSQLJDBC{jdbc:postgresql://localhost:5432/postgres}{postgres}{test}{testtable}%
%\dbCSVFile{result.csv}{test}

\begin{document}
\noindent
\sql{SELECT * FROM test;}\\[3pt]
The table ``test'' contains \dataText{SELECT COUNT(*) FROM test;} tuples.\\[3pt]
The following points are linked to the chart on the left side below: \dataText[linkTo=testname, linkSelector=2, linkLabel=Value at 2]{SELECT * FROM test WHERE a=2;}, \dataText[linkTo=testname, linkSelector=3, linkLabel=Value at 3]{SELECT * FROM test WHERE a=3;}.\\[3pt]
\chart[width=0.45\textwidth, height=0.3\textwidth, logscale=true, chartType=line, name=testname]{SELECT a, b, [attribute with space] FROM test;}
\chart[width=0.45\textwidth, height=0.3\textwidth, chartType=bar]{SELECT a, b, [attribute with space] FROM test;}\\[3pt]
{\fontfamily{phv} \tiny \selectfont
\noindent
Change the font before this line to Helvetica and fontsize to tiny.\\[3pt]
\chart[width=0.6\textwidth, height=0.25\textwidth, chartType=compareToBest]{SELECT b FROM test;}\\[3pt]
\multiplotChart[width=0.6\textwidth, height=0.5\textwidth, xCount=2, yCount=2, yValues={["b", "b*2"]}, xValues={["a <= 2", "a > 2"]}, topArr={["a smaller or equal 2", "a greater 2"]}, yFirst]{SELECT a,? FROM test WHERE ?;}\\[3pt]
\pivotTable[width=0.10\textwidth, height=0.15\textwidth, rows={["a"]}, aggregationattribute=b]{SELECT * FROM test;}
\dataTable[verticalLines=i, horizontalLinesHeader=b hh, horizontalLinesBody=i]{SELECT * FROM test;}\\[3pt]
}
\end{document}

### 2016-02-10 pdbf-doc.tex
- fixed a bug that sometimes made the xref fixing fail - minified all js and css files - updated lot of javascript libraries to up to date versions

\section{Thanks to}
phantomJS (\url{https://github.com/ariya/phantomjs})\\
Apache Commons (\url{http://commons.apache.org/})\\
Apache PDFBox (\url{https://pdfbox.apache.org/})\\
jTar (\url{https://github.com/kamranzafar/jtar})\\
google-gson (\url{https://github.com/google/gson})\\
postgreSQL JDBC Driver (\url{https://jdbc.postgresql.org/})\\
MariaDB JDBC Driver (\url{https://mariadb.com/kb/en/mariadb/about-the-mariadb-java-client/})\\
AlaSQL (\url{https://github.com/agershun/alasql})\\
C3 (\url{https://github.com/masayuki0812/c3})\\
D3 (\url{https://github.com/mbostock/d3})\\
Codemirror (\url{https://github.com/codemirror/codemirror})\\
google-diff-match-patch (\url{https://code.google.com/p/google-diff-match-patch/})\\
explorercanvas (\url{https://code.google.com/p/explorercanvas/})\\
DataTables (\url{https://github.com/DataTables/DataTables})\\
jQuery (\url{https://github.com/jquery/jquery})\\
jQuery-UI (\url{https://github.com/jquery/jquery-ui})\\
jStat (\url{https://github.com/jstat/jstat})\\
pivottable (\url{https://github.com/nicolaskruchten/pivottable})\\
PDF.js (\url{https://github.com/mozilla/pdf.js})\\
google-closure-compiler (\url{https://github.com/google/closure-compiler})\\
lz-string (\url{https://github.com/pieroxy/lz-string})\\

>>>>

\section{Thanks to}
phantomJS (\url{https://github.com/ariya/phantomjs})\\
Apache Commons (\url{http://commons.apache.org/})\\
Apache PDFBox (\url{https://pdfbox.apache.org/})\\
jTar (\url{https://github.com/kamranzafar/jtar})\\
google-gson (\url{https://github.com/google/gson})\\
postgreSQL JDBC Driver (\url{https://jdbc.postgresql.org/})\\
MariaDB JDBC Driver (\url{https://mariadb.com/kb/en/mariadb/about-the-mariadb-java-client/})\\
AlaSQL (\url{https://github.com/agershun/alasql})\\
C3 (\url{https://github.com/masayuki0812/c3})\\
D3 (\url{https://github.com/mbostock/d3})\\
Codemirror (\url{https://github.com/codemirror/codemirror})\\
google-diff-match-patch (\url{https://code.google.com/p/google-diff-match-patch/})\\
explorercanvas (\url{https://code.google.com/p/explorercanvas/})\\
DataTables (\url{https://github.com/DataTables/DataTables})\\
jQuery (\url{https://github.com/jquery/jquery})\\
jQuery-UI (\url{https://github.com/jquery/jquery-ui})\\
jStat (\url{https://github.com/jstat/jstat})\\
pivottable (\url{https://github.com/nicolaskruchten/pivottable})\\
PDF.js (\url{https://github.com/mozilla/pdf.js})\\
google-closure-compiler (\url{https://github.com/google/closure-compiler})\\
lz-string (\url{https://github.com/pieroxy/lz-string})\\
YUI Compressor (\url{https://github.com/yui/yuicompressor})\\
